\bf Model Visualization Techniques for a Social Network Model

### 2017-08-24 paper.Rnw
remove some unnecessary comments

For comparison, we also fit models $M1$, $M2$, and $M3$ to the senate collaboration data. Comparison of the parameter estimates of these models fit to the two different data sets is given in Table~\ref{tab:meanests} In addition, we fit two more models, $M4$ and $M5$ to the senate data that were found to be significant according to the Wald-type test:

@@

XXX TO DO - working on model estimates tonight XXX

>>>>

For comparison, we also fit models $M1$, $M2$, and $M3$ to the senate collaboration data. Comparison of the parameter estimates of these models fit to the two different data sets is given in Table~\ref{tab:meanests}. In addition, we fit two more models, $M4$ and $M5$ to the senate data that were found to be significant according to the Wald-type test:

@@
